pirouette: Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-03-18 article.tex

"What is the error made by BEAST2 from a phylogeny, 
when hand-picking an inference model, compared to the background noise?"

@@

Most of the settings for this example research question are
the same as in the previous section, which are
the phylogeny from an unknown speciation model (listing~\ref{lst:unknown_phylogeny}), 
the alignment parameters (listing~\ref{lst:create_alignment}) 
and the list of experiments (listing~\ref{lst:create_generative_experiment}).

\iffalse
This time, however, we are interested in creating a twin tree,
as such a twin tree allows us to measure a baseline error produced
by the BEAST2 run.
A twin tree
has the same topology as the given tree, 
yet its branching times are simulated according 
to a tree prior already implemented by BEAST2 to produce a posterior. 
Because for a twin tree we know the tree prior 
and because we use that tree prior in inference, 
we expect BEAST2 to produce a posterior of phylogenies
that is close to the twin tree.
As the inference model for the twin tree is (more) completely
specified than the true tree, 
we expect that a twin tree and its posterior trees are more similar
than a true tree and its posterior trees.
Due to this, the twinning is used a control for the experiment.
\fi

This time, however, we are interested in creating a twin tree. A twin tree
has the same topology as the given tree, yet its branching times are simulated according to the standard tree prior used by BEAST2 to produce the posterior for the main pipeline. 
Since there is coherence between the inference model and the generative model, we expect BEAST2 to produce a posterior of phylogenies more similar to the original one, respect to the outcome of the main pipeline. 
Due to this, the twinning process is used to provide a control for the main experiment.

>>>>

"What is the error made by BEAST2 from a phylogeny, 
when hand-picking a tree prior, compared to the background noise?"

@@

Most of the settings for this example research question are
the same as in the previous section, which are
the phylogeny from an unknown speciation model (listing~\ref{lst:unknown_phylogeny}), 
the alignment parameters (listing~\ref{lst:create_alignment})
and the list of experiments (listing~\ref{lst:create_generative_experiment}),
the latter stating that the generative tree prior is a Yule tree prior.

This time, however, we are interested measuring both the inference error
and a baseline error, which is achieved by creating a twinning parameter
set. 
This time, however, we are interested in creating a twin tree. A twin tree
has the same topology as the given tree, yet its branching times are simulated according to the standard tree prior used by BEAST2 to produce the posterior for the main pipeline. 
Since there is coherence between the inference model and the generative model, we expect BEAST2 to produce a posterior of phylogenies more similar to the original one, respect to the outcome of the main pipeline. 
Due to this, the twinning process is used to provide a control for the main experiment.
